---
title: "POST ICO Analysis"
output:
    html_document


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo = FALSE, warning = FALSE, message = FALSE}

suppressPackageStartupMessages(library('rvest'))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(remedy))  # very useful for Markdown formatting

tkn_price <- 0.0320
Token <- "neo"
p1 <- "https://coinmarketcap.com/currencies/"
p2 <- "/#markets"

path <- paste(p1, Token, p2 , sep = "")

url <- (path)

markets <- url %>%
    read_html() %>%
    html_nodes(xpath='//*[@id="markets-table"]') %>%
    html_table()

markets <- markets[[1]]


eth <- url %>%
        read_html() %>%
        #html_nodes(xpath='/html/body/div[2]/div/div[1]/div[4]/ul/li[3]/a')   #can be used if changes on the website
        html_nodes(xpath='/html/body/div[2]/div/div[1]/div[3]/ul/li[3]/a')

eth <- eth[[1]]

ETH_scan_url <- xml_attrs(eth)[["href"]]

### Data cleaning   ###

#change Exchanges to Factors
markets$Source <- as.factor(markets$Source)

#remove * from trading volume
markets$`Volume (24h)` <- gsub("[[:punct:]]", "", markets$`Volume (24h)`)
markets$`Volume (24h)` <- as.integer(markets$`Volume (24h)`)

#remove $,* from price
markets$Price <- gsub( "\\$", "", markets$Price )
markets$Price <- gsub( "\\*", "", markets$Price )
markets$Price  <- as.double (markets$Price)

#convert Volume(%) to %
markets$`Volume (%)` <- substr(markets$`Volume (%)`,1,nchar(markets$`Volume (%)`)-1)
markets$`Volume (%)` <- as.double(markets$`Volume (%)`)


### Statistics  ###

#number of exchanges 
exs <- paste("The " , toupper(Token), " is traded on ", length(unique(markets$Source)), " exchanges" , sep = "")

#top 5 exchnages
top_5_ex <- markets %>% 
    group_by(Source) %>% 
    summarise( share = sum(`Volume (%)`) ) %>% 
    arrange(desc(share)) %>% 
    top_n(5)
top_5_exchanges_share <- sum(top_5_ex$share)
top_5_exchanges_names <- as.character(top_5_ex$Source)

top_5_ex$Source <- as.character(top_5_ex$Source)
shr <- 100-top_5_exchanges_share
oth <- c("Other", shr)
top_5_ex[6,] <- oth


t <- list(
  family = "sans serif",
  size = 18,
  color = 'black')


p_ex <- plot_ly(top_5_ex, labels = ~top_5_ex$Source, values = ~as.double(top_5_ex$share), type = 'pie',
                textposition = 'inside',
                textinfo = 'percent+label',
                insidetextfont = list(color = '#FFFFFF'),
                hoverinfo = 'text',
                direction = 'clockwise',
                marker = list(colors = colors,line = list(color = '#FFFFFF', width = 0.5))) %>%
        layout(font=t,showlegend = F,
           xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
           yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

top_e <- paste("The top exchange for ",toupper(Token), " is ", top_5_exchanges_names[1], " with the share of ", top_5_ex$share[1], "%",sep = "")

#top 5 currencies

#distinguish Currencies
    splt <- strsplit(markets$Pair,split='/', fixed=TRUE)
    splt <- unlist(splt)
    markets$Pair <- splt[seq(2, length(splt), by = 2)] 
    markets$Pair <- as.factor(markets$Pair)
    
    top_5_cur <- markets %>% 
        group_by(Pair) %>% 
        summarise( share = sum(`Volume (%)`) ) %>% 
        arrange(desc(share)) %>% 
        top_n(5)
    
    top_5_cur_share <- sum(top_5_cur$share)
    top_5_cur_names <- as.character(top_5_cur$Pair)
    
    top_5_cur$Pair <- as.character(top_5_cur$Pair)
    shr_cur <- 100-top_5_cur_share
    oth <- c("Other", shr_cur)
    top_5_cur[6,] <- oth
    
    
   p_cur <-  plot_ly(top_5_cur, labels = ~top_5_cur$Pair, values = ~as.double(top_5_cur$share), type = 'pie',
                textposition = 'inside',
                textinfo = 'percent+label',
                insidetextfont = list(color = '#FFFFFF'),
                direction = 'clockwise',
                hoverinfo = 'text',
                marker = list(colors = colors,line = list(color = '#FFFFFF', width = 1))) %>%
        layout(font=t,showlegend = F,
           xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
           yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
   
top_c <- paste("The top the ",  "currency the ",toupper(Token), " is traded aginst is ", top_5_cur_names[1], " its share is ", top_5_cur$share[1], "%",sep = "")

markets <- markets[,2:6]
```

# Token `r Token`

<font face="Arial"> Link to CoinMarketCap -> `r path`</font>  
Link to EtherScan -> `r ETH_scan_url`


<font face="Arial">The **`r toupper(Token)`**  is traded on  **`r length(unique(markets$Source))`**  exchanges.</font>  
<font face="Arial">List of exchanges  **`r unique(markets$Source)`**.</font>  
<font face="Arial">The top exchange for **`r toupper(Token)`**  is  **`r top_5_exchanges_names[1] `**  with the share of **`r top_5_ex$share[1]`%**.</font>  
<font face="Arial">The top currency the **`r toupper(Token)`**  is traded against is **`r top_5_cur_names[1]`**, its share is **`r  top_5_cur$share[1]`%**.</font>

The top 20 traded Pairs on exchanges are listed below:

```{r} 

#head(markets,20)
```

## Top 5 Exchanges Shares  



```{r, echo=FALSE}
p_ex


```

## Top 5 Currency Shares  

```{r, echo=FALSE}

p_cur

```

## Current Financials

```{r, echo=FALSE, warning = FALSE, message = FALSE}
p_1 <- "https://coinmarketcap.com/currencies/"
p_2 <- "/historical-data/?start=20130428&end=20191220"

path_ <- paste(p_1, Token, p_2 , sep = "")

url <- (path_)

prices <- url %>%
    read_html() %>%
    html_nodes(xpath='//*[@id="historical-data"]/div/div[2]/table') %>%
    html_table()

prices <- prices[[1]]

#cleaning
prices$Volume <- gsub( "\\,", "", prices$Volume )
prices$Volume <- as.double(prices$Volume)

prices$`Market Cap` <- gsub( "\\,", "", prices$`Market Cap`  )
prices$`Market Cap`  <- as.double(prices$`Market Cap` )


#creating matrix
matrix <- matrix(1:9, nrow = 3, 
                 dimnames = list(c("Price","Market Cap","Trading Volume"), 
                                 c("Current","Minimum","Maximum")))

#price statistics
matrix[1,1] <- paste("$",format( round(prices$`Close**`[1],3), scientific=FALSE), sep = "")
matrix[1,2] <- paste("$",format(round(min(prices$`Close**`, na.rm = T),3), scientific=FALSE), sep = "")
matrix[1,3] <- paste("$",format(round(max(prices$`Close**`, na.rm = T),3), scientific=FALSE), sep = "")



#market cap statistics
x <- nchar ( min(prices$`Market Cap`, na.rm = T) )
n <- 10**  ( floor( (nchar ( min(prices$`Market Cap`, na.rm = T)))/3 ) *3 )
V <- ""

if (x<3) {
    V <<-''
}else if (x>=3 && x<6){
    V <<-'k'
}else if (x>=6 && x<9){
    V <<-'M'
}else if (x>=9 ){
    V <<-'bln'
}


matrix[2,1] <- paste("$",format(round(prices$`Market Cap`[1]/n,1), scientific=FALSE), V, sep = "")
matrix[2,2] <- paste("$",format(round(min(prices$`Market Cap`, na.rm = T)/n,1), scientific=FALSE), V, sep = "")
matrix[2,3] <- paste("$",format(round(max(prices$`Market Cap`, na.rm = T)/n,1), scientific=FALSE), V, sep = "")

#trading volume statistics
x <- nchar ( min(prices$Volume, na.rm = T) )
n <- 10**( floor( (nchar ( min(prices$Volume, na.rm = T)))/3 ) *3 )
V <- ""

if (x<3) {
    V <<-''
}else if (x>=3 && x<6){
    V <<-'k'
}else if (x>=6 && x<9){
    V <<-'M'
}else if (x>=9 ){
    V <<-'bln'
}


matrix[3,1] <- paste("$",format(round(prices$Volume[1]/n,1), scientific=FALSE), V, sep = "")
matrix[3,2] <- paste("$",format(round(min(prices$Volume, na.rm = T)/n,1), scientific=FALSE), V, sep = "")
matrix[3,3] <- paste("$",format(round(max(prices$Volume, na.rm = T)/n,1), scientific=FALSE), V, sep = "")

cnt_price <- prices$`Close**`[1]
ROI <- paste( "ROI = ", round((cnt_price-tkn_price)/tkn_price * 100,3), "%", sep = "")
```

<font face="Arial">ICO Price = $**`r tkn_price`**</font>  
<font face="Arial">**`r ROI`**</font>


```{r, echo=FALSE, warning = FALSE, message = FALSE}

matrix

 
```


```{r, echo=FALSE, warning = FALSE, message = FALSE}

Max_price <- round(max(prices$`Close**`, na.rm = T),3)

print ( paste0(" Max ROI was ", round((Max_price-tkn_price)/tkn_price * 100,2), "%", 
    " on ", prices$Date[prices$`Close**` == max(prices$`Close**`, na.rm = T)],
               "; token price was $", round(Max_price,2),
                                       " and 24h trading volume of $", round(prices$Volume[prices$`Close**` == max(prices$`Close**`, na.rm = T)]/1e6,2), "M",
                                       sep = ""))


print (ifelse ( min(prices$`Close**`) >= tkn_price, 
                paste0("The token price has never passed below the ICO level"),
                paste0( 'Price of the token was lower than ICO price ', round(length( prices$`Close**`[ prices$`Close**` < tkn_price] ) / length(prices$`Close**`) * 100,2),  
                  "% of trading time", " (", length( prices$`Close**`[ prices$`Close**` < tkn_price] ), " days)" )))


```
